---
title: "Working with Web Tracking Data - Tutorial"
author:
  - "Felix Schmidt"
  - "Maximilian Haag"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
source("../helpers.R")
```

# Introduction

In this code along, we will work with the Web Tracking data from the GESIS panel.dbd (Campusfile: [ZA5670](https://search.gesis.org/research_data/ZA5670)). We will cover data loading, cleaning, and basic analysis using R. Make sure you have downloaded the data and placed it in the `data/` folder as per the setup instructions.


# Setup

@TODO

# Topics
## Basics

For those less acquainted with computational methods, we begin with some basic examples so that you can familiarize yourself with browsing data. You will still need to install the packages and load the data as described above.

First, let’s get a feeling for the data: How many participants are in the data?


1. Load Campusfile
2. Linkage Merge survey data (demographics)


```{r}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

df <- read_csv2("../data/ZA5670_webtracking_data.csv")
glimpse(df)

df %>%
  summarise(
    n_rows = n(),
    n_panelists = n_distinct(panelist_id),
    missing_start_time = sum(is.na(start_time)),
    missing_host = sum(is.na(host))
  )
```
```{r}
survey_data <- read_csv2("../data/ZA5670_survey_data.csv")
glimpse(survey_data)

survey_data = survey_data %>% 
  dplyr::select(panelist_id, da119a_sex, da120a_ybrth, da127a_seduc)



# merge: many browsing rows + one survey row per panelist
data_full <- df %>%
  left_join(survey_data, by = "panelist_id")

glimpse(data_full)
```

## Working with URLs
1. extract DOMAIN from HOST


```{r}
data_full <- data_full %>%
  mutate(domain = adaR::ada_get_domain(paste0('https://', host)))


# Most common domains
data_full %>% 
  count(domain, sort = TRUE) %>% 
  head(20)
```




2. 



## Classify hosts (domains)
1. Merge GOND (German News List)

```{r}
gond <- openxlsx::read.xlsx("../data/GONDv3_domains.xlsx")
glimpse(gond)

gond = gond %>% 
  dplyr::filter(language=="de")

# We will join after we create `domain` from `host`.
# Expected: GOND has a column called `domain` (e.g., spiegel.de).
```

```{r}
# flag news domains
data_full = data_full %>% 
  mutate(is_news = if_else(domain %in% gond$domain,1,0))


# How many news visits are in the data?
prop.table(table(data_full$is_news))


# Most common news domains
data_full %>% 
  filter(is_news==1) %>% 
  count(domain, sort = TRUE) %>% 
  head(20)
```



2. Flag "search engines"

```{r}
search_engines <- c(
  "google.com", "google.de",
  "bing.com",
  "duckduckgo.com",
  "yahoo.com",
  "ecosia.org"
)

# flag news search_engines
data_full = data_full %>% 
  mutate(is_se = if_else(domain %in% search_engines,1,0))

```

```{r}
data_full %>%
  summarise(
    n_visits = n(),
    n_news_visits = sum(is_news, na.rm = TRUE),
    n_search_visits = sum(is_se, na.rm = TRUE),
    share_news = mean(is_news, na.rm = TRUE),
    share_search = mean(is_se, na.rm = TRUE)
  )

```

```{r}
prop.table(table(data_full$da120a_ybrth, data_full$is_news))
```



## Measures and Operationalisations (by panelist)
1. Duration of a visit
2. Number of news visits

```{r}
df_ind <- data_full %>%
  group_by(panelist_id) %>%
  summarise(
    n_visits = n(),
    news_visits   = sum(is_news, na.rm = TRUE),
    search_visits = sum(is_se,   na.rm = TRUE),
    .groups = "drop"
  )
```



summary(news_visits$news_visits)
news_visits %>% arrange(desc(news_visits)) %>% head(10)

3. Number of search engine visits

## Distributions (and Associations)
1. Build participant-level analysis dataset

For associations with survey variables, we build a one-row-per-person dataset.

```{r}
df_analysis <- survey %>%
  left_join(news_visits, by = "panelist_id") %>%
  left_join(search_visits, by = "panelist_id") %>%
  mutate(
    news_visits = replace_na(news_visits, 0),
    search_visits = replace_na(search_visits, 0)
  )

glimpse(analysis_df)
```



1. skewed distributions
2. political interest and news visits?

## Tasks
Do people with a high interest in politics visit news sites more often?


##

## 




...